### 2016-10-30 thesis/intro/intro.tex
tmp commit

\subsubsection{Individual-level (micro-level) factors}
\label{ssub:Individual-level (micro-level) factors}

@@

\subsubsection{Population-level (macro-level) factors}
\label{ssub:Population-level (macro-level) factors}

@@

One of the obvious factors that is linked to urbanisation is the lack of physical activity.
Currently, the recommended amount of physical activity to keep an individual fit and healthy is $\geq$ 150 min of moderate-intensity aerobic physical activity per week, or $\geq$ 30 min of physical activity on most days of the week \citep{Pate1995, WHO2010}.

sociocultural norm

\citep{Malik2013}\\

\noindent
The third factor is the income and socioeconomic status of the countries.
As mentioned briefly in the previous point, access to developed health care system will allow weight maintenance of the population, but most likely be of most benefit for the high-income group.
\textit{(Expand on this -- rise in income, availability of health care, etc.)}
\citep{Malik2013}\\

\noindent
The last factor, which ties in strongly with the first key factor, is the choice of diet by the population.
\textit{(Expand on this -- increased variety of food, low quality and high energy food choice, etc.)}

>>>>

\subsubsection{Individual-level (micro-level) factors}
\label{ssub:Individual-level_(micro-level)_factors}

@@

\subsubsection{Population-level (macro-level) factors}
\label{ssub:Population-level_(macro-level)_factors}

@@

Lack of physical activity is one of the obvious components that contribute to obesity, which is also linked with the urbanisation of the population.
Currently, the recommended amount of physical activity to keep an individual fit and healthy is $\geq$ 150 min of moderate-intensity aerobic physical activity per week, or $\geq$ 30 min of physical activity on most days of the week \citep{Pate1995, WHO2010}.
However, in many urban cities, this recommended level of physical exercise is difficult to achieve and maintain, due to the shift towards the sedentary behaviours that are encouraged by the developed transport system, automated household chores, and indoor entertainment \citep{Malik2013}.

It is unfair for urbanisation to take all of the blame for the lack of exercise in the population, but it is true that urbanisation makes the bar higher for many people to take up the recommended level of exercise and maintain it.\\

\noindent
The third factor is the income and socioeconomic status of the population.
As the average income increases, more people are able to buy food and are likely to take up the sedentary lifestyle.
Clearly, these behavioural changes will increase the likelihood of becoming obese.

From this, one would expect the high-income group to have the largest impact from obesity, but on the contrary to this expectation, the biggest impact from obesity is seen in the low- and middle-income groups of the population \citep{Malik2013}.
As mentioned briefly earlier, access to the developed health care system will allow weight maintenance of the population, but this is likely to be of most benefit for the high-income group in the population.
The reason for this is, quite simply, the cost associated with the visit to the health care system.
and therefore high-income group are more likely to make a visit than the low or middle-income group of the population \citep{Malik2013}.

So, for the low- and middle-income groups, the rise in average income in these groups allow the people to have access to food and activities that promotes sedentary bahaviours, but the limited access to the health care system, education and recreational activities that promote physical activites ultimately leads to positive energy balance and obesity \citep{Malik2013}.
In contrast, the high-income group of the population have better access to the facilities that promote weight maintenance, thus have less of an impact from obesity compared with the low- and middle-income groups of the population.\\

\noindent
The last factor, which ties in strongly with the first key factor, is the choice of diet made by the population.
The amount of low-quality food have increased significantly in many rapidly growing countries, as these high-energy, low-nutritional food are cheaper and more profitible than the natural produce that have higher nutritional value (citation).
As a result, more people tend to purchase these low-quality food more often, and consume more energy than they are required.

Many people eat responsibly and avoid these low-quality diet and prevent overconsumption of such food.
However, the overconsumption of these food is not a big problem as such, but rather the overall quality of the food \citep{Malik2013}.
These food are usually high in refined sugar and unhealthy fat, highly processed, contain very little nutritional value and low in fibre.
Thus consuming these food, especially food that are high in saturated fats,

The abundance of food that are high in energy and low in nutritional value have increased significantly.
In contrast to this, the amount of  natural produces have decreased.

\textit{(Expand on this -- increased variety of food, low quality and high energy food choice, etc.)}

\citep{Malik2013}
\\
